Exploring probability distributions for bivariate temporal granularities

### 2019-12-07 main.Rmd
cyclic gran section full update

**Example**: \autoref{fig:aperiodic-example} shows two aperiodic linear granularity $M_1$ and $M_2$. Each granule is represented by a box. The diagram also illustrates that the granules that overlap share elements from the underlying time domain. The first slot in the diagram shows the index set and A_{B, M} consists of three categories, one corresponding to the first aperiodic event $M_1$, the second corresponding to aperiodic event $M_2$ and the third corresponding to no event/aperiodic linear granularity.

>>>>

**Example**: \autoref{fig:aperiodic-example} shows two aperiodic linear granularity $M_1$ and $M_2$. Each granule is represented by a box. The diagram also illustrates that the granules that overlap share elements from the underlying time domain. The first slot in the diagram shows the index set and $A_{B, M}$ consists of three categories, $L(1)$ corresponding to the first aperiodic event $M_1$, $L(2)$ corresponding to aperiodic event $M_2$ and the $L(0)$ corresponding to no event/aperiodic linear granularity.
